---
title: "Assessment 1.2"
author: "Kyle Beall"
date: "5/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
#install.packages("skimr")
library(skimr)
```

#Data Wrangling

```{r}
# number 3
fast_food<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

fast_food%>%skim()
```

```{r}
# number 4
fast_food%>%count(restaurant)

```

```{r}
# number 5
fast_food%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))%>%
  ungroup()

# number 6
fast_food<-
  fast_food%>%
  group_by(restaurant)%>%
  mutate(average_calories=mean(calories))%>%
  ungroup()

```

```{r}
# number 7
fast_food%>%
  ggplot(
    aes(total_fat)
  )+
  geom_histogram()+
  facet_wrap(vars(restaurant))
```


7. Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. **

8. Display the count of observations per each type of restaurant

9. Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 

10. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 

- Save your .rmd file 

- Do a commit in Git tab

- Push in the same tab

